\chapter*{Acknowledgments}
\label{chp:0-acknowledgments}

I would like to acknowledge the support I was given by my supervisor
Prof. Daniel Kressner. His clear guidance and unparalleled expertise were the
critical success factor for my thesis. I appreciate him always being very generous
with his time despite his full schedule. In every meeting he filled my hands with
ideas, inspiration, and appropriate criticism. He assigned me a tasks on which
I worked well beyond the usual eight hour workday; not because I had to, but because
I wanted to and enjoyed every moment of doing so. I am grateful for all the
opportunities and favours he has given me during this time.\\

My co-supervisor, Haoze He, also contributed heavily to me having a great time
these last four months. With his tolerance for my mistakes, quick grasp of
complicated concepts, and critical thinking skills he was able to support me
well in my work. Our many shared interests led to uncountable
entertaining conversations. Our collaboration together with Hysan Lam, who
also helped me in countless ways, was to me one of the most exciting parts of
my work.\\

I am thankful for all the amazing people I could meet during my thesis.
The many interesting conversations I was able have over lunch with
the other members of the ANCHP group, namely David, Peter,
Margherita, Angelo, and Nian, always inspired and entertained me.
The fact that they treated me as one of them made me feel accepted and gave 
me the confidence to pursure my goals.\\

Furthermore, I express my gratitude for my teachers, family, and friends.
If it was not for the many teachers who have inspired, mentored, and formed me
all my life long, I would not have been motivated to pursue this path.
My parents were always there for me and stood behind me no matter what I did.
Being able to count on their kindness and support helped me overcome multiple
challenging situations. Thanks to my friends I could experience many great moments and adventures
during the time of working on my thesis, particularly with Lucas, Jozef, Bruno,
Irvin, Mateja, Bartul, and Paride.\\ 

Finally, I admit that the title image of this thesis was inspired
by the album cover of Joy Division's studio album called Unknown Pleasures.
It is a schematic depiction of the spectral densities of 15 different Gaussian random matrices.
